Value-Suppressing Uncertainty Maps

### 2017-03-22 paper/template.tex
Dealt with often.
Update template.tex

Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \textbf{uncertainty-aware decisions}--- that is, the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \textbf{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset. Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map--- a relation, in terms of visual variables, between a 2-tuple $(value$,$uncertainty)$ and a set of marks. The design of bivariate maps is difficult and, due to the interference and interplay between different visual variables, often leads to maps with very few discriminable categories.

In this paper, we present \textbf{Value-Suppressing Uncertainty Maps} (VSUMs) for integrating data and uncertainty information in thematic maps. VSUMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a traditional two dimensional bivariate map, with unique outputs for each relevant combination of data and uncertainty, VSUMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. Figure \ref{fig:example} shows an example of a VSUM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSUMs, examples of their utility for decision-making under uncertainty, and validate that VSUMs in a crowd-sourced experiment.

>>>>

Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \textbf{uncertainty-aware decisions}--- that is, the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \textbf{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset. Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map--- a relation, in terms of visual variables, between 2-tuples $(\text{value}, \text{uncertainty})$ and mark properties. The design of bivariate maps is difficult and, due to the interference and interplay between different visual variables, often leads to maps with few discriminable categories.

In this paper, we present \textbf{Value-Suppressing Uncertainty Maps} (VSUMs) for integrating data and uncertainty information in thematic maps. VSUMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a traditional two dimensional bivariate map, with unique outputs for each relevant combination of value and uncertainty, VSUMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. Figure \ref{fig:example} shows an example of a VSUM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSUMs, examples of their utility for decision-making under uncertainty, and validate that VSUMs TODO in a crowd-sourced experiment.
